---
title: "fuzzy_join()"
author: "Tony Fujs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The fuzzy_join() function merges datasets that don't have any common id to merge them on. For instance, two different datasets can contain both `first name`, and `last name` information, but due to typos, discrepancies will exist between the two datasets.   

## STEP 1: Load the data sets to be merged
```{r, fig.show='hold'}
data(eto)
head(eto)

data(nwea)
head(nwea)
```

Both data sets contains `first name` and `last name`. We will create a custom id variable based on names.

## STEP 2: Create custom id variable

```{r, fig.show='hold'}
eto$my_id <- create_id(eto, var = c('lname', 'fname'))
head(eto)

nwea$my_id <- create_id(nwea, var = c('StudentLastName', 'StudentFirstName'))
head(nwea)
```


## STEP 3: Merge both datasets

```{r, fig.show='hold'}
df <- fuzzy_join(x = nwea, y = eto, by = 'my_id')

head(df)
```

Both data sets have been merged. A new variable `match_status` identifies whether the match was `perfect`, `partial`, or if the record was `unmatched`


> "Thanks @psychemedia for most of the code"
([via](http://blog.ouseful.info/2012/09/26/merging-data-sets-based-on-partially-matched-data-elements/))
